article title

### 2022-07-08 article.tex
Add theorems, corrolaries
Use package hyperref
Add hyperlinks

@@

% useful for definitions, theorems, corollaries, etc.
\theoremstyle{myenv}
\theoremstyle{mytheorem}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{axiom}[theorem]{Axiom}
\theoremstyle{mydefinition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{question}[theorem]{Question}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}

@@

@@

@@

\newpage
\section{Bold, italics, and underline}
\label{sec:bold_italics_underline}
Bold text is done with \textbackslash{textbf\{\textless text \textgreater\}} such as \textbf{bolded text}.

Italics text is done with \textbackslash{textit\{\textless text \textgreater\}} such as \textit{italics text}.

Underline text is done with \textbackslash{underline\{\textless text \textgreater\}} such as \underline{italics text}.

Bold and italics text is done with \textbackslash{textbf\{\textbackslash{textit\{\textless text \textgreater\}\}} such as \textbf{\textit{bolded text}}.

Some of the \textbf{greatest} \textit{discoveries} in \underline{science} were made by \textbf{\textit{accident}}.

\section{Lists}
Unordered list
\begin{itemize}
    \item Illinois
        \begin{itemize}
            \item Chicago
            \item Naperville
        \end{itemize}
    \item Kentucky
        \begin{itemize}
            \item Lexington
            \item Louisville
        \end{itemize}
\end{itemize}

@@

% H means 'here definitely' to place the figure
\begin{figure}[H]
\label{fig:anatomy_of_a_matplotlib_figure}
% \includegraphics[width=\textwidth, inner]{matplotlib_anatomy_of_a_figure}
\includegraphics[width=3in, left]{matplotlib_anatomy_of_a_figure}
\caption{Anatomy of a matplotlib figure}
\end{figure}

@@

\begin{theorem}[Fundamental Theorem of Calculus]
\label{thm:ftc}
If $f$ is continuous on the interval $[a,b]$, then \[\frac{d}{dx}\int_a^x f(t)dx=f(x)\] for all $a\le x\le b$.
\end{theorem}

@@

\section{Still to do}
\label{sec:still_to_do}

\subsubsection{Not started}
\label{sec:even_more_to_do}
- matrices

@@

\newpage
\section{Acknowledgement}
\label{sec:acknowledgement}

>>>>

% very useful for hyperlinks
\usepackage{hyperref}

@@

% useful for definitions, theorems, corollaries, etc.
\theoremstyle{myenv}
\theoremstyle{mytheorem}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{axiom}[theorem]{Axiom}
\theoremstyle{mydefinition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{question}[theorem]{Question}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}
\makeatletter
\@addtoreset{theorem}{section}
\makeatother

@@

% create a list of theorems command
\newcommand{\listtheoremsname}{List of Theorems}
\newlistof{mytheorems}{thm}{\listtheoremsname}
\newcommand{\mytheorems}[1]{%
\addcontentsline{thm}{mytheorems}{\protect\numberline{\thetheorem}#1}\par}
\renewcommand{\cftthmtitlefont}{\normalfont\Large\bfseries}

@@

% create a list of corollaries command
\newcommand{\listcorollariesname}{List of Corollaries}
\newlistof{mycorollaries}{cor}{\listcorollariesname}
\newcommand{\mycorollaries}[1]{%
\addcontentsline{cor}{mycorollaries}{\protect\numberline{\thecorollary}#1}\par}
\renewcommand{\cftcortitlefont}{\normalfont\Large\bfseries}

@@

\newpage
\section{Bold, italics, and underline}
\label{sec:bold_italics_underline}
Some of the \textbf{greatest} \textit{discoveries} in \underline{science} were made by \textbf{\textit{accident}}.

\section{URLs}
\label{sec:urls}
Hyperlinks within the document can be easily added. For example, see Graphics \ref{sec:graphics} and Anatomy of a matplotlib figure \ref{fig:anatomy_of_a_matplotlib_figure} and Definition of a limit \ref{def:limit}.

Hyperlinks to external URLs can be easily added. For example, see \href{https://en.wikipedia.org/wiki/Latex}{Wikipedia \LaTeX}.
\section{Lists}
Unordered list
\begin{itemize}
    \item Illinois
        \begin{itemize}
            \item Chicago
            \item Naperville
        \end{itemize}
    \item Kentucky
        \begin{itemize}
            \item Lexington
            \item Louisville
        \end{itemize}
\end{itemize}

@@

% H means 'here definitely' to place the figure
\begin{figure}[H]
% \includegraphics[width=\textwidth, inner]{matplotlib_anatomy_of_a_figure}
\includegraphics[width=3in, left]{matplotlib_anatomy_of_a_figure}
\caption{Anatomy of a matplotlib figure}
\end{figure}
\label{fig:anatomy_of_a_matplotlib_figure}

@@

\begin{theorem}[Fundamental Theorem of Calculus]
\label{thm:ftc}
If $f$ is continuous on the interval $[a,b]$, then \[\frac{d}{dx}\int_a^x f(t)dx=f(x)\] for all $a\le x\le b$.
\end{theorem}
\mytheorems{Fundamental theorem of calculus}

\section{Corollaries}
\label{sec:corollaries}
\begin{corollary}
If $f$ is continuous on the interval $[a,b]$, then \[\int_a^b f(x)dx=F(b)-F(a)\] where $F$ is any antiderivative of $f$.
\end{corollary}
\mycorollaries{f is continuous}

@@

@@

\newpage
\listofmytheorems

\newpage
\listofmycorollaries

\newpage
\section{Acknowledgements}
\label{sec:acknowledgements}
